Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-16 paper.tex
update

In section \ref{background}, we first describe the target language we will
analyze and a concrete CESK machine as operational semantics for it.
Then we review abstracting abstract machines (AAM) as an abstract interpretation
counterpart of CESK machines.

@@

%probably Store Widening \& Abstract Garbage Collection
\section{To Direct-Style}

>>>>

In section \ref{background}, we first describe the target language we will
analyze and a concrete CESK machine as small-step operational semantics for it.
Then we review abstracting abstract machines (AAM) as an abstract interpretation
counterpart of CESK machines. In section \ref{linear}, we convert the
non-deterministic choices of closures to another layer of continuations,
therefore linearize the abstract execution.
Section \ref{fusing} fuses the driver function and step function to one single
function.
In section \ref{disen}, we further identify the first-order data type representations of
continuations, and disentangle the code blocks for dispatching data types to separate
functions.
Section \ref{refunc} represents the refunctionalized abstract abstract machines,
In this part, the continuations represented by data type trun to higher-order
functions.
In Section \ref{directstyle}, we transform the refunctionalized AAM to two
different direct style, one is implemented with monads, the other is using
delimited controls.

\todo{Add section numbers to the figure}

@@

%probably Store Widening \& Abstract Garbage Collection
\section{To Direct-Style} \label{directstyle}
